%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Ashton Foley} \\ \vspace{1pt}
    28140 Galien Dr, South Lyon, MI 48178 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 734-436-9967 ~ \href{mailto:foleyash0@umich.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{foleyash@umich.edu}} ~ 
    \href{https://linkedin.com/in/ashtonfoley}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/ashtonfoley}}  ~
    \href{https://github.com/foleyash}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/foleyash}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Michigan}{September 2022 -- May 2025}
      {Bachelor of Science in Engineering for Computer Science (GPA: 3.9)}{Ann Arbor, MI}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\textbf{Activities}{: Michigan Hackers Open Source Development Team Lead} \\
\textbf{Relevant Coursework}{: Web Systems, Database Management Systems, Computer Networks, Theory of Computer Science, Computer Hardware, Data Structures and Algorithms, Differential Equations, Linear Algebra}

%-----------PROGRAMMING SKILLS-----------
\section{Programming Languages, Technologies, and Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, JavaScript/TypeScript, C\#, HTML/CSS, SQL, Matlab} \\
     \textbf{Technologies/Frameworks}{: AWS, React, Linux, Git, Node.js, Docker, Jira, Bitbucket, Jenkins, .NET} \\
     \textbf{Skills}{: Full Stack Development, Automated Testing, API Development, Database Design, OOP, Cloud Computing, AGILE} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {United Wholesale Mortgage}{May 2024 - August 2024}
      {DevOps Engineer Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Designed and implemented an ASP.NET microservice integrated with Bitbucket's API, facilitating the collection and transmission of millions of data entries to the company's data lake, enhancing data availability and analysis capabilities.}
        \resumeItem{Implemented robust exception handling mechanisms within the microservice, ensuring seamless application performance and reliability. Integrated logging of exceptions to Dynatrace for proactive monitoring and issue resolution.}
        \resumeItem{Developed a PowerShell script consumed by the Octopus pipeline, automating the removal of testing databases during deployment workflows to reduce unnecessary storage overhead.}
        \resumeItem{Streamlined several Jenkins build pipelines by refactoring outdated steps, resulting in cleaner and more efficient code.}
        \resumeItem{Contributed effectively to several Agile teams, utilizing Jira for task management and progress tracking, ensuring alignment with project timelines and delivering comprehensive weekly progress reports.}
    \resumeItemListEnd 
    \resumeSubheading
      {Ride or Dial, Contract}{August 2023}
      {Back End Web Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Investigated an ongoing outage in the company's web application on the server-side and developed a lasting solution by reconfiguring their nginx server and renewing outdated certificates to resume their business quickly and conveniently.}
    \resumeItemListEnd    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Spotify Shared Queue Platform} $|$ \emph{Typescript, PostgreSQL, Next.js, React, Docker}}{February 2024 - April 2024}
          \resumeItemListStart
            \resumeItem{Designed and developed a Next.js web application integrated with Spotify's API, enabling users to securely share access to their music queue through trusted sessions.}
            \resumeItem{Implemented a complex application architecture involving REST APIs and Websockets to orchestrate session management and engineer data pipelines.}
            \resumeItem{Utilized the React framework to maintain a seamless user experience, crafting reusable components that interfaced efficiently with backend systems.}
            \resumeItem {Developed a shell script to automate PostgreSQL database setup from within a Docker container, expediting the development process.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Slide-n-stack.com} $|$ \emph{JavaScript, HTML, CSS, MySQL, Express, AWS}}{May 2023 -- August 2023}
          \resumeItemListStart
            \resumeItem{Built and deployed a full stack arcade-style game to the web using a combination of front-end (HTML, CSS, JavaScript), back end (Node.js, Express, MySQL), and infrastructure (AWS) technologies.}
            \resumeItem{Developed a neat, immersive gameplay experience using HTML, CSS, and JavaScript to mimic the classic arcade feel.}
            \resumeItem{Utilized the express framework to develop a RESTful API that sends and retrieves user data from a MySQL database using HTTP requests and JSON data formatting.}
            \resumeItem{Developed a user authentication portal that allows users to login and create accounts that will track their top scores and report their placement to the leaderboard, using the JavaScript library bcrypt to encrypt user passwords.}
            \resumeItem{Deployed to the web using AWS ec2 to run both the Node.js application and its MySQL server entirely in the cloud.}
            \resumeItem{Configured nginx as a reverse proxy to route domain requests to a secured server using HTTPS.}
          \resumeItemListEnd
          \vspace{-13pt}
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}
